---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Conor Lacey"
date: "02-04-2023"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
suppressWarnings(library(tidyverse))
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r dennys-dataset, message = FALSE}
dn<-dennys
nrow(dn)
ncol(dn)
```

In the dennys dataset, there are 1,643 row and 6 columns. Each row represents an individual dennys location. The variables in this data set include...

```{r dennys-variables}
colnames(dn)
```


### Exercise 2

Now let's look at the La Quinta dataset.

```{r laquinta-dataset}
lq<-laquinta
nrow(lq)
ncol(lq)
```

The La Quinta dataset has 909 rows and 6 columns. Each row represents one La Quinta location. The variables in the dataset are as follows: 

```{r laquinta-variables}
colnames(lq)
```

### Exercise 3

Going to the La Quinta website there are La Quinta's outside the U.S. that include Canada, Mexico, China, New Zealand, Turkey, United Arab Emirates, Chile, and Columbia. 

Going to the Denny's website it was actually difficult to find information on locations outside the U.S. Fortunately, statista.com provides data on this if you follow this link: https://www.statista.com/statistics/947495/number-of-dennys-restaurants/
  
From this link we find that there are Denny's outside the U.S. that include Canada, Puerto Rico, Mexico, Phiippines, New Zealand, Honduras, United Arab Emirates, Guatemala, Costa Ric, Guam, Indonesia, El Salvador, United Kingdom, Aruba, Curacao N.V., and the Domincan Republic. 
  
### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

