---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Conor Lacey"
date: "02-04-2023"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
suppressWarnings(library(tidyverse))
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r dennys-dataset, message = FALSE}
dn<-dennys
nrow(dn)
ncol(dn)
```

In the dennys dataset, there are 1,643 row and 6 columns. Each row represents an individual dennys location. The variables in this data set include...

```{r dennys-variables}
colnames(dn)
```


### Exercise 2

Now let's look at the La Quinta dataset.

```{r laquinta-dataset}
lq<-laquinta
nrow(lq)
ncol(lq)
```

The La Quinta dataset has 909 rows and 6 columns. Each row represents one La Quinta location. The variables in the dataset are as follows: 

```{r laquinta-variables}
colnames(lq)
```

### Exercise 3

...

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

